\vspace{-0.8in}Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms

### 2016-02-12 podc16/paper2.tex
Checked with TLC that the graph processing formalization in the brief announcement is correct.

\textbf{Lemma 1}
Assume that: $g_1$ and $g_2$ are two dependency graphs; 
for every pair of non-commutative commands $c_1,c_2 \in V\left(g_2\right)$, either $\left( c_1,c_2 \right)\in E\left( g_2 \right)$ or $\left( c_2,c_1 \right)\in E\left( g_2 \right)$;
$g_1 \leq g_2$; \todo{Instead of the previous one: $g_1$ and $g_2$ are compatible};
$l_1$ is a linearization of $g_1$ and $l_2$ is a linearization of $g_2$. 
Then we have (a), $\bot\bullet l_1 \sqsubseteq \bot\bullet l_2$, and (b), if $g_1 = g_2$ then $\bot\bullet l_1 = \bot\bullet l_2$.

@@

\subsection{Consistency and Liveness}
\textbf{Lemma 2}
If $g_p^1$ is the graph $g_p$ at time $t_1$, $g_q^2$ is the graph $g_q$ at time $t_2$, and $t_1 \leq t_2$, then $g_p^1 \leq g_q^2$.
\todo{This is wrong\ldots
What about: If $g_p^1$ is the graph $g_p$ at time $t_1$, $g_q^2$ is the graph $g_q$ at time $t_2$, and $t_1 \leq t_2$, then $g_p^1$ and $g_q^2$ are compatible.}

>>>>

\textbf{Lemma 1}
Assume that: $g_1$ and $g_2$ are two dependency graphs; 
for every pair of non-commutative commands $c_1,c_2 \in V\left(g_2\right)$, either $\left( c_1,c_2 \right)\in E\left( g_2 \right)$ or $\left( c_2,c_1 \right)\in E\left( g_2 \right)$;
$g_1 \leq g_2$; \todo{Instead of the previous one: $g_1$ and $g_2$ are compatible};
$l_1$ is a linearization of $g_1$ and $l_2$ is a linearization of $g_2$. 
Then we have (a), $\bot\bullet l_1 \sqsubseteq \bot\bullet l_2$, and (b), if $g_1 = g_2$ then $\bot\bullet l_1 = \bot\bullet l_2$.
\todo{No, then we have that $\bot\bullet l_1$ and $\bot\bullet l_2$ are compatible.}

@@

\subsection{Consistency and Liveness}
\textbf{Lemma 2}
If $g_p^1$ is the graph $g_p$ at time $t_1$, $g_q^2$ is the graph $g_q$ at time $t_2$, and $t_1 \leq t_2$, then $g_p^1 \leq g_q^2$.
\todo{This is wrong\ldots
What about: If $g_p^1$ is the graph $g_p$ at time $t_1$, $g_q^2$ is the graph $g_q$ at time $t_2$, then $g_p^1$ and $g_q^2$ are compatible.}

\textbf{Lemma 3}
Consider $g_1$ and $g_2$. Assume that if $v\in V\left( g_1 \right)$ and $v\in V\left( g_2 \right)$ then $n\left( g_1 \right)=n\left( g2 \right)$.

\textbf{Lemma 4}
If $m_p\subseteq m_q$
